Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2022-11-22 Manuscript/SupMaterial.Rmd
Added Table 3: Model fit

>>>>

## Interaction strength distribution

The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions. Table 3 shows the results for the six candidate models used.

load("../Manuscript/ModelFit.rda")
knitr::kable(IS_fit %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web. Order by best fit. References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit. Log-Normal is the best model.")
